Observation of falling snow orientation in sheltered and unsheltered observation sites

### 2024-07-09 Grazioli_JGRA_2024.tex
Updates from Overleaf

\authors{J. Grazioli\affil{1}, M. Condolf\affil{2}, F. Coletti\affil{2}, and A. Berne\affil{1}  }

\affiliation{1}{Environmental Remote Sensing Laboratory, École Polytechnique Fédérale de Lausanne, Lausanne, Switzerland}
\affiliation{2}{Department of Mechanical and Process Engineering, ETH, Zürich, Switzerland}
% \affiliation{3}{Third Affiliation}

@@

\begin{keypoints}
\item Observations of falling snowflake orientations show symmetrical distributions around 0°, aligning with some previous literature assumptions.
\item Sheltered and unsheltered sites show differences in orientation distributions, influenced by wind. Instrument (local perturbations) and atmospheric effects cannot be separated.
\item Numerical simulations reveal previously reported non-zero median orientations as artifacts, identifying better estimation methods.
\end{keypoints}

\begin{abstract}
This study investigates the orientation of falling snowflakes using data from a Multi-Angle Snowflake Camera (MASC). We explore the impact of different observational setups (sheltered vs. unsheltered), wind conditions, hydrometeor type, and axis ratio on the orientation distributions. Numerical simulations are used to select the best orientation estimator and to understand the reason behind different results reported in past literature. We find that previously reported non-zero median orientations are likely artifacts of averaging absolute values from individual cameras. Observed orientations generally follow a symmetrical distribution around 0$^\circ$, with broader and flatter distributions observed in unsheltered sites and high wind conditions.  Observed distributions may vary significantly from those assumed in previous studies, highlighting the need for further research on snowflake orientation under varying environmental conditions.
\end{abstract}

@@

\section{Introduction}
Ice-phase hydrometeors, individual crystals and aggregates fall with a preferred orientation; In stable conditions, they align in a way that maximizes the area projected in the direction of flow~\cite{Koebschall_EF_2023}. This fact is exploited by dual-polarization weather radars to retrieve information about the microphysical processes occurring in precipitation and to identify which type of hydrometeors are present and where. Except for relatively rare situations, like storm electrification~\cite<e.g.,>{Krehbiel_MAP_1996,Pineda_JGRA_2019}, the interpretation of radar meteorology rely on the assumption that anisotropic ice particles tend to fall with their major dimension oriented horizontally.
The concept of orientation is thus linked to the anisotropic nature of most hydrometeors and it loses any meaning for isotropic, spherical particles.

Considering a population of hydrometeors rather than individual particles, as it is often the case for practical applications, the distribution of orientations is often modeled with a relatively narrow variability around 0$^\circ$ (i.e., horizontally oriented) values. Looking at the overview of Table~\ref{table:orientations}, one can observe that modeling studies mostly employ a Gaussian distribution, with standard deviations varying between 3$^\circ$~\cite<e.g.>{Matrosov_JAM_2001} and 60$^\circ$~\cite<e.g.>{Putnam_MWR_2017} depending on the type of hydrometeors.  
Observational studies~\cite<as in>{Garrett_GRL_2015} confirmed that there are differences due to hydrometeor type but also due to the environmental conditions (wind and turbulence). Observational studies report non-zero mean and median orientation values, which is contradictory with what stated so far. As we will discuss later in this manuscript, this discrepancy is in reality the result of the way multi-view instrumental observations are combined to retrieve an individual estimate of orientation.

The problem of observing hydrometeor orientations while they fall, without generating disturbance induced by the measurement itself, is not trivial. Among the ground-based instruments able in principle to perform this task we may cite: the two-dimentional video disdrometer~\cite<2DVD>{Kruger_JAOT_2002}, the multi-angle snowflake camera~\cite<MASC>{Garrett_AMT_2012}, the Precipitation Imaging Package~\cite<PIP>{Pettersen_atmosphere_2020} and the latest Video In Situ Snowfall Sensor~\cite<VISSS>{Maahn_AMT_2024}. All relatively recent, they differ for example for the number of simultaneous viewpoints (one for PIP, three for MASC, two for the others), resolution (order of magnitudes of tens of $\mu{m}$ for MASC and VISSS and hundreds of $\mu{m}$ for 2-DVD and PIP) or instrumental structure (compact for MASC and 2-DVD and open for PIP and VISSS). These sensors allow for direct investigations, based on the pictures of individual hydrometeors. As mentioned above, indirect retrievals  of the behaviour of large populations of particles within the sampling volume of remote-sensing instruments are also commonly employed, mostly by means of dual-polarization technologies~\cite<e.g.,>{Matrosov_JAS_2005},

In this manuscript we present an analysis of fall orientation of ice-phase hydrometeors, conducted on a large dataset collected by a MASC. We explore the effect of different siting of the instrument (sheltered or unsheltered), wind conditions, hydrometeor type and axis ratio as well as the estimator of orientation used. For the last investigation, We complement the analysis with simulations aimed at uncovering biases that may emerge with some estimation choices.

\section{Data and Methods}
We use a large dataset of MASC data which includes co-located environmental information, notably  temperature, humidity, wind, from the MASCdb database described in~\cite{Grazioli_SD_2022}. The database currently includes about one million of image triplets (e.g. Fig.~\ref{fig:triplet}) and pre-computed geometrical and microphysical descriptors. In this study, we filter the initial database to: (i) remove precipitation falling at positive temperatures, as we focus on dry snow; (ii) we remove particles classified as \textit{small particles} according to the classification of~\cite{Praz_AMT_2017} as their size is too close to the resolution of the images  (about 35$\mu$m); (iii) we remove all the measurements possibly due to wind-blown snow according to~\cite{Schaer_TC_2020}. All the filtering steps are conducted on data already integrated in MASCdb, thus readily reproducible. The filtered dataset includes 412'150 particles.

While operating with three 2D images of and individual 3D object, the first issue is to obtain one estimate of orientation to assign the the object/snowflake. As snowflakes are often modeled as ellipsoids or spheroids, previous studies on the MASC used the orientation of the major axis of the best-fitting ellipsoid as a proxy for orientation in individual 2D images~\cite{Garrett_GRL_2015,Gergely_JGRA_2016, Fitch_AMT_2021, Fitch_JGR_2022}, and then taking the mean of the absolute value of the three estimates. We refer to this approach to \textit{Mean\_Abs}. Other studies perform instead a 3D reconstruction of an ellipsoid that best fits the three views, and take as estimate the orientation of the major axis of such ellipsoid~\cite{Jiang_JAS_2019}. We refer to this family of approaches as \textit{Ellipsoid\_Fit}. At a first glance in Table~\ref{table:orientations}, the results of the experimental studies using those estimators seem to disprove the common assumption that the distribution of orientations of snowflakes is centered at 0$^\circ$, and modal values between 10$^\circ$ and 20$^\circ$ are reported. While for the \textit{Ellipsoid\_Fit} in ~\cite{Jiang_JAS_2019} this is based on a small sample of aggregates, thus difficult to evaluate, we would like to show that the appearance of non-zero modal values in the \textit{Mean\_Abs} approach is a bias induced by conducting this type of averaging.

To do so, and to select an appropriate estimator of orientation, we conducted numerical simulations (results shown in Fig.~\ref{fig:simulations}). Ellipsoid of randomly varying geometry as well as simulated aggregates and monomers are generated~\cite<as for example in>{Leinonen_AMT_2021} and their projection into MASC-like images is computed in order to test various estimation methods. The orientation of the reference snowflakes or ellipsoid is individually known and it is drawn by a zero-mean and 25$^\circ$ standard deviation from a Gaussian distribution. While this simulation setup has the potential to be exploited much further than this with the variations of all the parameters involved, the goal is here to support the selection of the estimator that we will employ in the actual field-collected data. Figure~\ref{fig:simulations} allows us to have an overview of how well various methods reproduce the distribution of orientation (panel a,c) and the magnitude of the errors with respect to the absolute value of the orientation (panel b, d). We tested the following estimator: \textit{Min}, being the minimum (absolute value) orientation among the views with sign preserved, \textit{Mean\_Abs} as defined above, \textit{Ellipsoid\_fit} as described above, \textit{Mean} being the mean of the estimate of three views, as well as the individual estimates of each view \textit{Cam0}, \textit{Cam1}, \textit{Cam2}.

The results of this experiment shows first of all that the non-zero modal values of \textit{Mean\_Abs} appear also in this case, thus confirming the hypothesis that this is an artefact of averaging absolute-values, which makes near-zero estimates much less likely to occur. \textit{Ellipsoid\_fit} has small errors, but the modal values of the distribution of this method consistently show a positive bias of a few degrees, such that the reconstructed distribution is not centered exactly at 0$^\circ$. Individual camera views have larger errors as well as very broad reconstructed distributions, a result in itself interesting and worth investigating further as many snowflake imagers have only one view. \textit{Min} provides low errors, but it produces distributions that are exaggeratedly leptokurtic. Therefore in the following, we will use a simple \textit{Mean}, which is an optimal compromise between preserving as much as possible the shape of the distribution with limited errors and extreme simplicity. For this specific experimental setup, \textit{Mean} is also the only method that likely preserves Gaussianity, according to a Kolmogorov-Smirnov test.

\section{Experimental results and discussion}
The distribution of all the (\textit{Mean}) orientation values presented in Fig.~\ref{fig:alldata} shows that the overall distribution is symmetrical with a mode at 0$^\circ$. The distribution of all observations is fat-tailed. Different type of instrument installations have a clear impact on the distribution: installations within DFIRs, with enhanced wind sheltering and protection from local turbulence shows less pronounced tails while not sheltered sites more pronounced ones as well as a much flatter distribution in the proximity of 0$^\circ$ orientation values, between -25$^\circ$ and 25$^\circ$. It can be hypothesized that this change in shape of the distribution is the result of the different siting, with the unsheltered observations perturbed by \textit{local} turbulence driven by the instrument itself~\cite<as described by>{Fitch_AMT_2021}.

It is however reasonable to assume that the \textit{atmospheric} conditions should play a role in shaping the distribution of orientation values, with broader distribution in case of strong winds and wind variations. In Fig.~\ref{fig:wind-effect} we compare the evolution of the standard deviation of orientation distributions for DFIR and unsheltered conditions at various levels of horizontal winds. At low winds ($<1$ms$^{-1}$), the curves are relatively close, as well as for high winds ($>10$ms$^{-1}$) while they depart up to 5/6$^\circ$ for intermediate conditions, with the DFIR curve increasing as the wind increases. It can be assumed that for near-zero winds local turbulence due to the instrument itself is minimal, and sheltered and unsheltered conditions are substantially equivalent. It is however not straightforward to interpret the behaviour of the curves in case of stronger winds. One explanation could be that as the wind gets stronger, the DFIR shelter gets less effective, leading to a broadening of the distribution (broadening due to local interactions with the instrument). However, strong wind conditions could broaden the distribution as well (broadening due to atmospheric causes) and a combination of the two mechanisms is plausible. Further research would be needed to clarify this aspect and for the time we can simply report this discrepancy among the different siting types.

Under the assumption that measurements collected within a DFIR are inherently less perturbed, we focus now the attention only on this type of siting. Given the large size of the original dataset, we can perform further data stratification. Figure~\ref{fig:hydroclass} shows the distribution of orientations in two contrasting wind regimes ($<4$ms$^{-1}$ and $>8$ms$^{-1}$), stratified according to hydrometeor type~\cite<method of>{Praz_AMT_2017} and average axis ratio of the particles (divided in two classes of below- and above-median axis ratio).  The effect of stronger winds results in broader and platykurtic distributions, which lose the clear median around 0$^\circ$ orientation values. For columnar and planar crystals of elongated shape (low axis ratio), this results in distributions that start to exhibit off-zero modal values, that are not observed in low-wind conditions. 
The effect of axis ratio on the distribution is not remarkable, but this is an important information in itself: we can exclude that the modal values around 0$^\circ$ may be artefacts resulting from near-spherical axis-symmetrical particles being assigned a quasi-horizontal orientations merely because of geometrical conventions.

If we focus only on low-wind conditions ($<4$ms$^{-1}$) within DFIR sites, a situation that should minimize perturbations for our dataset, the distribution of orientation values has $\sigma$ of 28$^\circ$ (graupel), 30$^\circ$ (aggregates), 32$^\circ$ (planar crystals), and 34$^\circ$ (columnar crystals), 29.5$^\circ$ (all mixed). Those values are within the range of commonly assumed ones, as reported in Table~\ref{table:orientations}, but depart significantly from individual studies especially the ones assuming extremely narrow distributions~\cite{Matrosov_JAM_2001,Matrosov_JAS_2005}, or the ones assuming much broader distributions~\cite<e.g.>{Ryzhkov_JAMC_2011, Bukovic_JAMC_2018}. Further research on the actual distribution of orientations is needed to fine-tune those estimates, especially in order to understand the effect of actual atmospheric conditions, not instrument-induced, on distribution shape and breadth.

\section{Conclusions}
The main results of this letter devoted to the estimation of the orientation of falling snowflakes with a MASC are:
\begin{itemize}
    \item Estimation of orientation as the mean of the orientation of the best fit ellipsoid of each camera views is a good compromise in terms of error minimization and correct reproduction of the distribution of orientation values. 
    \item Previous studies reporting median orientations departing from 0$^\circ$ are most likely resulting from artefacts due to averaging the \textit{absolute value} of the orientation of each camera view.
    \item Single-camera estimates are largely more uncertain than a combination of the three views.
    \item Field measurements on a large dataset show that orientation values have overall a symmetrical distribution around 0$^\circ$.
    \item Observations collected in unsheltered sites as well as in sheltered sites in strong wind conditions result in broader and flatter distributions, with a less clear mode at 0$^\circ$. This is probably both an artefact of local disturbances (instrument-induced) as well as actual environmental phenomenon. It is not possible in this set-up to separate the two effects and further research is needed in this field.
    \item Observed orientation distributions can differ largely with respect to assumptions made in previous studies. 
\end{itemize}

@@

% Giving latex a width will help it to scale the figure properly. A simple trick is to use \textwidth. Try this if large figures run off the side of the page.
\begin{figure}
 \noindent\includegraphics[width=\textwidth]{Fig01.png}
\caption{Example of a triplet of images of a snow aggregate, collected by a MASC. The best fitted ellipse of each image is drawn in green, with the major axis defining the apparent orientation with respect to the horizontal.    }
\label{fig:triplet}
\end{figure}

@@

\begin{figure}
 \noindent \centering \includegraphics[width=\textwidth]{Fig03.png}
\caption{Histogram of the distribution of orientation value for all data (412'150 particles, top) and data stratified according to the instrumental setup (bottom) either being unsheltered (274'839 particles) or deployed within a double-fence inter-comparison reference (DFIR, 137'311 particles). The dotted lines illustrate the shape of a Gaussian curve having the same mean and standard deviation as the observed data, and are given to provide a visual comparison of the difference with respect to a Gaussian shape (it is not a fit of the histogram). Orientation values are estimated as the sign-preserving mean of the three MASC views.   }
\label{fig:alldata}
\end{figure}

@@

@@

@@

\section{Open Research}
The MASCDB dataset used to reproduce the field-based results of this study is openly available in~\citeA{MASCDB_dataset_2023}

>>>>

%\authors{J. Grazioli\affil{1}, M. Condolf\affil{2}, F. Coletti\affil{2}, and A. Berne\affil{1}  }

%\affiliation{1}{Environmental Remote Sensing Laboratory, École Polytechnique Fédérale de Lausanne, Lausanne, Switzerland}
%\affiliation{2}{Department of Mechanical and Process Engineering, ETH, Zürich, Switzerland}
% \affiliation{3}{Third Affiliation}

@@

\begin{keypoints}
\item Observations of snowflake orientations show symmetrical distributions around 0$^\circ$ and standard deviations that confirm some of the assumptions made in non-observational studies. 
\item Sheltered and unsheltered sites show differences in orientation distributions, influenced by wind. Instrument (local perturbations) and atmospheric effects cannot be separated.
\item Numerical simulations reveal that common estimation choices made in past studies may lead to data processing artifacts.
\end{keypoints}

\begin{abstract}
This study investigates the orientation of falling snowflakes using data from a Multi-Angle Snowflake Camera (MASC). We explore the impact of different observational setups (sheltered vs. unsheltered), wind conditions, hydrometeor type, and axis ratio on the orientation distributions. Numerical simulations are used to select the best orientation estimator and to understand the reason behind different results reported in past literature. We find that previously reported non-zero median orientations are likely artifacts of averaging absolute values of apparent orientations from individual cameras. Observed orientations generally follow a symmetrical distribution around 0$^\circ$, with broader and flatter distributions observed in unsheltered sites and/or high wind conditions.  Observed distributions may vary significantly from those assumed in previous studies, highlighting the need for further research on snowflake orientation under varying environmental conditions.
\end{abstract}

@@

\section{Introduction}

Ice-phase hydrometeors, such as individual crystals and aggregates, fall with a preferred orientation. In stable conditions, they align in a way that maximizes the area projected in the direction of flow \cite{Koebschall_EF_2023}. This fact is exploited by dual-polarization weather radars to retrieve information about the microphysical processes occurring in precipitation and to identify which type of hydrometeors are present and where. Except for relatively rare situations, like storm electrification \cite{Krehbiel_MAP_1996,Pineda_JGRA_2019}, the interpretation of radar meteorology relies on the assumption that anisotropic ice particles tend to fall with their major dimension oriented horizontally. The concept of orientation is thus linked to the anisotropic nature of most hydrometeors and loses any meaning for isotropic, spherical particles.

Considering a population of hydrometeors rather than individual particles, as is often the case for practical applications, the distribution of orientations is often modeled with relatively narrow variability around 0$^\circ$ (i.e., horizontally oriented) values. Looking at the overview in Table~\ref{table:orientations}, one can observe that modeling studies mostly employ a Gaussian distribution model, with standard deviations varying between 3$^\circ$ \cite{Matrosov_JAM_2001} and 60$^\circ$ \cite{Putnam_MWR_2017} depending on the type of hydrometeors. Observational studies \cite{Garrett_GRL_2015} confirm that differences exist due to hydrometeor type and environmental conditions (wind and turbulence). Observational studies report as well non-zero mean and median orientation values, which is contradictory with what was stated previously. As we will discuss later in this manuscript, this discrepancy is, in reality, the result of the way multi-view instrumental observations are combined to retrieve an individual estimate of orientation.

The problem of observing hydrometeor orientations while they fall, without generating disturbance induced by the measurement itself, is not trivial. Among the ground-based instruments designed to perform this task, we may cite the two-dimensional video disdrometer (2DVD) \cite{Kruger_JAOT_2002}, the multi-angle snowflake camera (MASC) \cite{Garrett_AMT_2012}, the Precipitation Imaging Package (PIP) \cite{Pettersen_atmosphere_2020}, and the Video In Situ Snowfall Sensor (VISSS) \cite{Maahn_AMT_2024}. These relatively recent instruments differ, for example, in the number of simultaneous viewpoints (one for PIP, three for MASC, two for the others), resolution (on the order of tens of micrometers for MASC and VISSS and hundreds of micrometers for 2DVD and PIP), or instrumental structure (compact for MASC and 2DVD and open-field for PIP and VISSS). These sensors allow for direct microphysical investigations based on pictures of individual hydrometeors. As mentioned above, indirect retrievals of the behavior of large populations of particles within the sampling volume of remote-sensing instruments are also commonly employed, mostly by means of dual-polarization technologies \cite{Matrosov_JAS_2005}.

In this manuscript, we present an analysis of the fall orientation of ice-phase hydrometeors, conducted on a large dataset collected by a MASC. We explore the effect of different siting of the instrument (sheltered or unsheltered), wind conditions, hydrometeor type, and axis ratio, as well as the estimator of orientation used. For the last investigation, we complement the analysis with simulations aimed at uncovering biases that may emerge with some estimation choices.

@@

\section{Data, Methods, Preliminary Considerations}

We utilize a large dataset of MASC observations, which includes co-located environmental information such as temperature, humidity, and wind, sourced from the MASCdb database extensively described in \cite{Grazioli_SD_2022}. The MASC instrument~\cite{Garrett_AMT_2012} captures simultaneous images of falling snowflakes with three cameras looking at a common focal point from three different viewpoints (0$^\circ$, +36$^\circ$, -36$^\circ$).

MASCdb includes approximately one million image triplets (see Fig.~\ref{fig:triplet}) and pre-computed geometrical and microphysical descriptors. For the purpose of the present study, we filter the initial dataset by: (i) excluding precipitation occurring at positive temperatures, focusing thus on dry snow; (ii) removing particles classified as \textit{small particles} following the criteria in \cite{Praz_AMT_2017}, due to their size being too close to the image resolution (which is about 35$\mu$m); and (iii) excluding measurements potentially affected or dominated by wind-blown snow according to \cite{Schaer_TC_2020}. All filtering steps are conducted on data already integrated into MASCdb, ensuring reproducible results. The resulting filtered dataset comprises 412'150 particles.

\begin{figure}
 \noindent\includegraphics[width=\textwidth]{Fig01.png}
\caption{Example of a triplet of images of a snow aggregate, collected by a MASC. The best fitted ellipse of each image is drawn in green, with the major axis defining the apparent orientation with respect to the horizontal.    }
\label{fig:triplet}
\end{figure}

In handling three 2D images of an individual 3D object, a primary challenge is to derive a single  estimate of orientation for each snowflake. Snowflakes are commonly modeled as ellipsoids or spheroids in previous MASC studies: the orientation of the major axis of the best-fitting ellipsoid in each 2D image is estimated, and the average of the three views is considered as a proxy for orientation \cite{Garrett_GRL_2015, Gergely_JGRA_2016, Fitch_AMT_2021, Fitch_JGR_2022}. The cited studies calculate the mean of the absolute value of the three estimates, an approach referred to here as \textit{Mean\_Abs}. Alternatively, other studies perform a 3D reconstruction of the ellipsoid that best fits all three views and take the orientation of its major axis as the estimate \cite{Jiang_JAS_2019}, a family of approaches named \textit{Ellipsoid\_Fit}. Examining Table~\ref{table:orientations}, the experimental studies using these estimators report the occurrence of non-zero modal orientation values between 10$^\circ$ and 20$^\circ$, challenging the common assumption of a distribution centered at 0$^\circ$. While the non-zero modal values reported for \textit{Ellipsoid\_Fit} in \cite{Jiang_JAS_2019} are based on a small sample of aggregate snowflakes, making evaluation difficult, we demonstrate that the appearance of non-zero modal values in the \textit{Mean\_Abs} approach results simply from averaging absolute values. This will offer a reconciliation between the common assumptions made on snowflake orientations and the contradiction of the first studies that used the MASC, a contradiction that was observed also by~\citeA{Garrett_GRL_2015} and discussed in the Conclusions of their works.

To address this, and to select an appropriate orientation estimator, we conducted numerical simulations (results shown in Fig.~\ref{fig:simulations}). These simulations generated ellipsoids with randomly varying geometries, as well as more realistic and geometrically complex aggregates following methods such as those described in \cite{Leinonen_AMT_2021}. The objects, of known 3D structure are projected into MASC-like 2D images to test various estimation methods. The orientation of the reference snowflake or ellipsoids is known and drawn from a Gaussian distribution with a zero mean and 25$^\circ$ standard deviation. Although this simulation setup could be expanded extensively to investigate the contribution of each ingredient at play, the goal here is to support the selection of an estimator to use with actual field-collected data. Figure~\ref{fig:simulations} provides an overview of how various methods reproduce the orientation distribution (panels a and c) and the magnitude of errors relative to the absolute orientation value (panels b and d). Tested estimators include: \textit{Min}, representing the minimum (absolute value) orientation among the views with preserved sign; \textit{Mean\_Abs}, as previously defined; \textit{Ellipsoid\_Fit}, as described; \textit{Mean}, the mean of the estimates from the three views; and individual estimates from each view (\textit{Cam0}, \textit{Cam1}, \textit{Cam2}).

@@

The result of the simulations reveal that the non-zero modal values observed with \textit{Mean\_Abs} are artifact resulting from averaging absolute values,  reducing the likelihood of near-zero estimates. With an example: let us assume that the individual estimate of orientation from the three cams were -10$^\circ$, 0$^\circ$ and +20$^\circ$. With \textit{Mean\_Abs} the final estimate would be approximately 10$^\circ$, while for \textit{Mean} it would be roughly 3$^\circ$. The results shown here show that, at least statistically-speaking, a bias is introduced.

The \textit{Ellipsoid\_Fit} method exhibits small errors but its distribution consistently shows a positive bias of a few degrees, making it not centered precisely at 0$^\circ$. Individual camera views yield larger errors and broader distributions, which is in itself a noteworthy result given that many snowflake imagers only capture one view. \textit{Min} provides low errors but produces distributions that are excessively leptokurtic. Consequently, for subsequent analyses, we adopt a straightforward \textit{Mean}, which is possibly an optimal balance between preserving distribution shape with minimal errors and simplicity. Importantly, \textit{Mean} is the only method in this specific experimental setup that likely maintains Gaussianity,  according to a Kolmogorov-Smirnov test.

\section{Experimental Results and Discussion}
The distribution of \textit{Mean} orientation values in field-collected data, as depicted in Fig.~\ref{fig:alldata}, reveals an overall symmetrical distribution centered at 0$^\circ$. However, the distribution has fat tails with the frequency of large orientation values exceeding the ones of a Gaussian of equivalent standard deviation. The installation conditions of the instruments significantly influence this distribution: sites within Double-Fence Intercomparison Reference~\cite<DFIR, see for example>{Smith_HESS_2020}, providing enhanced wind sheltering and protection from local turbulence, show less pronounced tails. In contrast, unsheltered sites exhibit more pronounced tails and a flatter distribution near 0$^\circ$, ranging between -25$^\circ$ and 25$^\circ$. This suggests that unsheltered observations are likely perturbed by local turbulence induced by the instrument itself, as described in~\citeA{Fitch_AMT_2021}.

\begin{figure}
 \noindent \centering \includegraphics[width=0.8\textwidth]{Fig03.png}
\caption{Histogram of the distribution of orientation value for all data (412'150 particles, top) and data stratified according to the instrumental setup (bottom) either being unsheltered (274'839 particles) or deployed within a double-fence inter-comparison reference (DFIR, 137'311 particles). The dotted lines illustrate the shape of a Gaussian curve having the same mean and standard deviation as the observed data, and are given to provide a visual comparison of the difference with respect to a Gaussian shape (it is not a fit of the histogram). Orientation values are estimated as the sign-preserving mean of the three MASC views.   }
\label{fig:alldata}
\end{figure}

Atmospheric conditions are expected to play a role in shaping orientation distributions, particularly increasing wind conditions. Figure~\ref{fig:wind-effect} compares the standard deviation of orientation distributions between DFIR and unsheltered sites at different wind speeds. At low wind speeds ($<1$ ms$^{-1}$) and high wind speeds ($>10$ ms$^{-1}$), the curves are close. However, they diverge by up to 5/6$^\circ$ for intermediate wind speeds, with the DFIR curve showing an increase with wind speed once the wind speed exceeds 4 ms$^{-1}$ and being relatively constant below that threshold. Under near-zero wind conditions, local turbulence induced by the instrument geometry is minimal, making DFIR and unsheltered conditions comparable. One hypothesis could be that until 4 ms$^{-1}$ the DFIR is effective in minimizing local turbulence (DFIR curve constant, unsheltered curve abruptly increasing), while it gradually loses this capacity until "saturating" around 10 ms$^{-1}$ (DFIR curve increasing, unsheltered curve constant). Making this assumption is however implying that all the observed variations is due to the instrument itself and not a physical phenomenon of interaction of turbulent air and snowflakes.  Further research is therefore necessary to clarify these dynamics.

@@

Given that the measurements within DFIRs are less perturbed, we focus now on this siting type. With the original dataset's large size, we conduct further data stratification. Figure~\ref{fig:hydroclass} illustrates orientation distributions under two contrasting wind regimes ($<4$ ms$^{-1}$ and $>8$ ms$^{-1}$), stratified by hydrometeor type~\cite{Praz_AMT_2017} and average axis ratio. Stronger winds lead to broader and platykurtic distributions, where a clear median around 0$^\circ$ orientation values is less evident and the distribution starts to assume uniform shape. For elongated columnar and planar crystals (low axis ratio), this results in distributions showing off-zero modal values, which were not observed under low-wind conditions.

The influence of axis ratio on distribution is not significant, but this is an important information. It allows to exclude that the observed distribution could be an artefact given by the convention of assigning 0$^\circ$ orientation values to particles with axis ratio of 1. As the shape of the distribution is preserved for low and high axis ratios, we can be confident of the physical nature of this distribution shape. 
 Focusing on low-wind conditions ($<4$ ms$^{-1}$) within DFIR sites, i.e. the subset with minimal external perturbations, the orientation distribution exhibits standard deviations of 28$^\circ$ (graupel), 30$^\circ$ (aggregates), 32$^\circ$ (planar crystals), and 34$^\circ$ (columnar crystals), with a combined value of 29.5$^\circ$ for all types. These values align with commonly assumed ranges (Table~\ref{table:orientations}), yet differ notably from individual studies employing extremely narrow or broad distributions~\cite{Matrosov_JAM_2001, Matrosov_JAS_2005, Ryzhkov_JAMC_2011, Bukovic_JAMC_2018}. Future research should refine these estimates, particularly to discern the impact of actual atmospheric conditions versus instrument-induced effects on distribution shape and breadth.

@@

\section{Conclusions}
The main results of this study on the estimation of the orientation of falling snowflakes using a MASC are summarized as follows.
At first, estimating orientation as the mean of the orientation of the best-fit ellipsoid from each camera view represents a reasonable approach in terms of minimizing errors and accurately reproducing the distribution of orientation values. Single-camera estimates exhibit high uncertainty compared to combining estimates from all three views and this should be kept in mind if single-view imagers are used. Previous studies reporting median orientations deviating from 0$^\circ$ in MASC studies are likely artifacts resulting from averaging the \textit{absolute value} of orientation estimates from each camera view. This explication, demonstrated with numerical simulations in the manuscript, is simpler than what proposed for example by~\cite{Garrett_GRL_2015} who hypothesized fluttering and local, instrument-induced, turbulence (which has anyway an impact) as possible explanations. 
Field measurements from a large dataset demonstrate that orientation values generally exhibit a symmetrical distribution around 0$^\circ$. Observations from unsheltered sites or in very high wind conditions result in broader and flatter orientation distributions, with a less pronounced mode at 0$^\circ$. This is likely influenced by both local disturbances (instrument-induced) and environmental factors, although with the current information we can only observe this discrepancy.
It is clear that further research, with different setups is needed to separate the contributions of these effects and estimate the \textit{natural} effect of wind and turbulence on the distribution of orientation values. Finally, we observed that orientation distributions of some hydrometeor types can vary significantly with respect to the assumptions made in previous studies.

\section{Open Research}
The MASCDB dataset used to for the field-based data of this study is openly available in~\citeA{MASCDB_dataset_2023}. The scripts to reproduce the results in this manuscript are openly available at \hl{TODO: add github repo with the scripts}.

% Giving latex a width will help it to scale the figure properly. A simple trick is to use \textwidth. Try this if large figures run off the side of the page.

@@
